Constant-round Blind Classical Verification of Quantum Sampling

### 2021-05-31 blind.tex
Sync Overleaf changes
Sync to GitHub for 1st submission

%Our compiler is a straightforward way of achieving blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},
%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

\Ethan{``preserves soundness" needs just a bit more discussion, since all we've proven are two experiments being identical.}

\begin{thm}
    Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{thm}

\begin{thm}
        Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
        %There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors under the QLWE assumption.
\end{thm}

>>>>

\begin{thm}
    Assuming the QLWE assumption, \Ethan{wording sounds awkward? Maybe ``under the QLWE assumption"...?} there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{thm}

\begin{thm}
        Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
\end{thm}

### 2021-05-31 introduction.tex
Sync to GitHub for 1st submission

>>>>

\Ethan{Related QIP review below:

A potential problem I see is that the main theorem (Theorem 1.1) in the paper gives a protocol that achieves only computational soundness.  Roughly speaking, this means that the protocol can only be used to verify that the ideal distribution is close to some distribution which in turn is computationally indistinguishable from the ideal quantum distribution.  This guarantee seems not to be enough for any currently established (or conjectured!) hardness argument in quantum supremacy.  The problem is essentially that quantum hardness of sampling arguments are fundamentally only (potentially) robust to statistical distance and not computational indistinguishability.  For example, it would be fully compatible with everything we know (and even quite expected) if the output distribution of random quantum circuits are, with high probability over the choice of random circuit, *computationally indistinguishable* from the uniform distribution.  But clearly the uniform distribution is n!
 ot hard to sample from.

Said in another way: what is being shown here is the following: consider a new class sampBQP', where the complete problem is to sample from something BQP-indistinguishable from the output distribution of a quantum circuit. Here it is shown that this new class sampBQP' can be interactively verified.  Unfortunately, we don’t know or have evidence that, for example $\SampBQP’ = \SampBPP \implies$ PH collapse, like we do for the standard sampBQP class.

Notably, discussion of this issue is missing entirely from the writeup!  In conclusion, while I found this paper to be an interesting followup to the Mahadev result, I find that the quantum supremacy motivation, which would a priori have been quite strong, is not obviously correct.}

### 2021-05-31 qpip0.tex
Sync to GitHub for 1st submission

Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that a accepted with mediocre probability. In \cite{arXiv:ChiaChungYam19}, this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying amplitude amplification to boost the accept probability if it is bigger than $\gamma$. However, states with accept probability really close to the threshold $\gamma$ can not be classified, so they need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
Now we give a formal description of the partition lemma.

@@

By Property~\ref{property:partition-testing} of \Cref{lem:partition2},
it clearly follows that 
\begin{claim}
	\label{lem:partition-testing}
	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
\end{claim}

@@

\begin{lemma}
	\label{thm:zi-zgoodi}
	\begin{align*}
	\tr\abs{z_i-z_{good, i}}\leq&\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]\\
	&+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).
	\end{align*}
\end{lemma}
\begin{proof}
    See \Cref{sec:qpip0}.
\end{proof}

>>>>

Also a careful reader might have noticed that the prover's space don't always decompose cleanly into parts that the verifier either rejects or accepts with high probability, as there might be some states that is accepted with mediocre probability. In \cite{arXiv:ChiaChungYam19}, this is solved by splitting the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$ and applying amplitude amplification to boost the accept probability if it is bigger than $\gamma$. However, states with accept probability really close to the threshold $\gamma$ can not be classified, so they need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.
Now we give a formal description of the partition lemma.

@@

By Property~\ref{property:partition-testing} of \Cref{lem:partition2},
it clearly follows that 
\begin{cor}
	\label{lem:partition-testing}
	For all $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and all $i,j\in[m]$ such that $j<i-1$, we have
	$$\norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2\leq (m-1)\gamma_0+\negl(n).$$
\end{cor}

@@

\begin{lemma}
	\label{thm:zi-zgoodi}
	\begin{align*}
	\tr\abs{z_i-z_{good, i}}\leq&\E_{pk, y, \gamma}\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}\R]\\
	&+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R).
	\end{align*}
\end{lemma}
\begin{proof}
    See \Cref{sec:qpip0}.
    \Ethan{Double check this ref? This feels off.}
\end{proof}
